True versus apparent shapes of bow shocks

### 2018-02-28 papers/Papers1234/sec-conclusions.tex
More on how results vary with Delta theta

The planitude is found to have a moderate dependence on the choice of
\(\Delta\theta\), as shown in Figure~~\ref{fig:000-400-Dtheta}. The fact that
the radius of curvature is defined at a point (the projected apex)
might seem to argue for making \(\Delta\theta\) as small as possible, but that
leads to an extreme sensitivity of the circle fits to the exact
positions of the few points that are included in the fit.  A reliable
fit requires 4 or more points, which span a total separation
\(\approx R_\C\).

>>>>

The planitude is found to have a moderate dependence on the choice of
\(\Delta\theta\), as shown in Figure~\ref{fig:000-400-Delta-theta}. The fact
that the radius of curvature is defined at a point (the projected
apex) might seem to argue for making \(\Delta\theta\) as small as possible, but
that would lead to circle fits that were extremely sensitive to the
exact positions of the few points included in the fit.  A reliable fit
requires 4 or more points, ideally spanning a total separation that is
a substantial fraction of \(R_\C\), which would argue for
\(\Delta\theta\) larger than about \(\Pi/2\) radians, or \ang{60}--\ang{90}.  On
the other hand, if \(\Delta\theta \ge \ang{90}\) then the planitude and alatude
would no longer be independent since the bow would be forced to lie on
the ``sphere'' line, \(\Lambda = (2 \Pi - 1)^{1/2}\) (see \S~\ref{sec:conic}).
Balancing these two concerns suggests an optimal
\(\Delta\theta = \ang{75}\), which is what is used in
Figure~\ref{fig:000-400-fit}, but we also show results for both
\ang{75} (thick lines) and \ang{60} (thin lines) in
Figure~\ref{fig:000-400-planitude-alatude}.

\(\Pi = 2.9 \pm 0.2 \pm 0.3\)
